Criticisms of the IHME COVID-19 model

### 2020-04-26 text/20/ihme-covid-model.Rmd
Updating 1999 posts

>>>>

Etzioni R, COVID-19 Models: What Makes Them Tick? Timmerman Report, 2020-04-07. Available in [html format](https://timmermanreport.com/2020/04/covid-19-models-what-makes-them-tick/).

+ This blog post describes how a theoretical model (the Imperial College model) works but uses a different term, mechanistic, and describes the model in greater detail. Then she discusses the atheoretical IHME model and again uses a different term than I do: empirical. The author draws a nice contrast and concludes that all models have weaknesses.
